
%--------------- List of Publications ---------------%


\chapter*{\fontsize{16}{16} \selectfont List of Publications}

%--------------- Journal Publications ---------------%
\vspace{-0.3in}
\begin{itemize}
\item \textbf{Published}

\begin{itemize}
\item International Journals
\begin{enumerate}
\item R. Pal and M. Saraswat, ``Histopathological image classification using enhanced bag-of-Feature with spiral biogeography-based optimization", \emph{Applied Intelligence}, 2019. (Online available, doi: https://doi.org/10.1007/s10489-019-01460-1)
\item R. Pal and M. Saraswat, ``Grey relational analysis based keypoint selection in bag-of-Features for histopathological image classification", \emph{Recent Patents on Computer Science}, vol. 12, pp. 1-6, 2018. 
\item R. Pal and M. Saraswat, ``Improved biogeography-based optimization", 				\emph{International Journal of Advanced Intelligence Paradigms}, 2017. (In press) 
\end{enumerate}
\item International Conferences
\begin{enumerate}
\item R. Pal and M. Saraswat, ``A new bag-of-feature method using biogeography-based optimization for categorization of histology images", in proc. of \emph{ International Conference on Computers and Management (ICCM)}, Delhi, India, pp. 155-160, 2018. 

\item R. Pal and M. Saraswat, ``Enhanced bag-of-features using AlexNet and improved biogeography-based optimization for histopathological image analysis", in proc. of \emph{IEEE International Conference on Contemporary Computing (IC3)}, Noida, India, pp. 1-6, 2018.
\item R. Pal and M. Saraswat, ``Data clustering using enhanced biogeography-based optimization", in proc. of \emph{IEEE International Conference on Contemporary Computing (IC3)}, Noida, India, pp. 1-6, 2017.
\end{enumerate}
\end{itemize}
\end{itemize}
\begin{itemize}
\vspace{1cm}

\item \textbf{Under Review}
\begin{enumerate}
 \item  R. Pal and M. Saraswat, ``Efficient Bag-Of-Features using grey relational analysis for Histopathology Image classification", \emph{Computers in Biology and Medicine}. 
\item   R. Pal and M. Saraswat, ``A New Weighted Two Dimensional Vector Quantization Encoding Method in Bag-of-Features for Histopathological Image Classification'', \emph{International Journal of Intelligent Information and Database Systems}. 
\end{enumerate}
\end{itemize}


