
%--------------- Abstract ---------------%

\begin{abstract}
Image classification is a process by which a machine can categorize the images into a finite set of classes. This process is applied to many important applications like robotics, remote sensing, optical character recognition, and medical image analysis. Histopathological image classification is also one of the prime areas of medical imaging in which changes in the tissue images are studied. However, due to the complex texture of histopathological images, it is generally done manually by the pathologists. Manual analysis is a time consuming and biased process. Therefore, in literature, several histopathological image classification methods are presented, out of which bag-of-features is one of the popular image categorization methods. However, due to the various morphological variability, available in the histopathological images, the bag-of-features method also lack in the classification accuracy and needed to be enhanced. Therefore, in this work, enhanced bag-of-features method is designed and developed for efficient histopathological image classification.

The work of this thesis is divided into five folds. First, a new computationally efficient keypoint selection phase is introduced in the bag-of-features method. Secondly,  two new variants of biogeography-based optimization algorithms are proposed and used to construct an optimal codebook. However, due to the high computation cost of biogeography-based optimization algorithms, the third part presents a new grey relational analysis based clustering method for obtaining the an efficient codebook. Fourth, a weighted two-dimensional vector quantization method has been presented for encoding the images. Finally, an enhance bag-of-features method for classification of histopathological images is designed and developed.

\textit{\textbf{Keywords:}} Histopathological image classification,  Bag-of-features,  Keypoints selection, Codebook construction, Biogeography-based optimization, Feature encoding.
\end{abstract}
