
%--------------- Acknowledgements ---------------%

\begin{acknowledgements}

I wish to express my deep gratitude to my supervisor Dr. Mukesh Saraswat. His precise and lucid thoughts have helped me to manage many responsibilities comfortably. He not only encouraged me to work but also gave his guidance, experience, constructive thoughts and took keen interest throughout the course of work and preparation of manuscript which had made me worth that I claim to be now. Working with him made me more independent and liable, which I believe is the most important aspect in anyone's career. I am indebted to him more than he recognize.

	No appropriate words could be traced in the presently available lexicon to avouch the excellent guidance given by Prof. S. C. Saxena, Vice-Chancellor, Prof. Hari Om Gupta, Director, Prof. D. K. Rai, Dean Academic, Prof. R. C. Mittal, Dean Research, Dr. Prof. S. P. Purohit, Controller of Examinations, and Prof. Vikas Saxena, Head of Department, Jaypee Institute of Information Technology, Noida for their constant support and full co-operation. Moreover, I would like to thank my research committee members and faculty members of the Institute for their help and support.

	 I am thankful to the Science and Engineering Research Board, Department of Science \& Technology, Government of India, New Delhi, India for funding this work as a part of the project (ECR/2016/000844). I am also thankful to Dr. J. C. Bansal, Dr. Harish Sharma, and Dr. Prashant Singh Rana for their suggestions and encouragement in problem domain had exceptionally enriched my growth. I am also thankful to Mr. Roop Singh Solanki to become part of the funded project.

	I am extremely thankful to Dr. Vinay Lomash who has given his constant guidance, support and encouragement throughout this study.  His expertise into the pathology, experience, vigorous efforts and co-operation had made me to complete this work. Without his unfailing support and belief in me, this thesis would not have been possible.

	I am extremely thankful Dr. Charu Gandhi, Prof. Krishna Asawa, Dr. Anuj Bhardwaj, Dr. Pankaj Srivastava, Dr. Dinesh Bisht, Dr. Shashi Bhushan, Dr. A. K. Malik, Dr. Suryakant, Dr. Aruna Malik, and Dr. Aarti   for their constant guidance, support and encouragement throughout this study. Their expertise, valuable suggestions and co-operation had made me complete this work.
	
	 I am sincerely thankful to my friends Mr. Himanshu Mittal, Mr. Ashish Kumar Tripathi, Mr. Ankur Kulhari, Mr. Avinash Pandey, Mr. Pushpendra Kumar Rajput  for their scholastic guidance, suggestions and encouragement throughout the study duration. Along with them, I am also thankful to Mr. Sudhanshu Kulshrestha, Mrs. Anuradha Gupta, Mrs. Parul Agrawal, Mrs. Vartika Srivastva, Mrs. Bindu Verma and other colleagues for providing their kind helps and supports during the time of research.

	I would also like to acknowledge the help rendered by Mr. Kirpal Singh, Mr. Abhishek Verma, Mr. Netra Pal, Mr. Gavendra Singh, Mr. Prashant Kumar, and Mr. Upendra Dubey for their day-to-day assistance and contribution, which made my work easier. It is my great privilege to mention the entire official staff for helping me in the official documentation work right from the time of my registration into Ph.D.

	I would like to offer my most humble gratitude to my parents (Shri Brijmohan Pal and Smt. Yashoda Pal), my sister Rajni, my nephews Aarush and Aadwik, my wife Surbhi, and other family members for their unsurpassed love, care, endless patience and countless sacrifices which they made for me. Indeed, a plethora of words would not suffice to say what I owe to them.

And above all I am blessed by Lord Shri Salasar Balaji Maharaj for giving me the strength and perseverance to toil towards this accomplishment without any hardships.


\begin{flushright}
    Raju Pal
\end{flushright}

\end{acknowledgements}

